---
title: "Provably Anonymous Covid Survey"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal

A demonstration of how anyone can be surveyed in a provably trustless and anonymous manner through adding noise to the response by using Randomised Responses.

## An Embarrassing Question

Suppose I asked you, a very sensitive question.

Randomised Response Surveys are conducted in the following manner:

1. An embarrassing question is posed to the participant.
2. Participants flip a coin before they answer. 
3. We instruct them to answer truthfully, if it comes up heads and YES if it comes up tails.

Only the participant knows if their YES is a result of a tails coin toss or their truthful answer. 

In the aggregate, we expect to see more than 50% of "yes" responses. If done as a census, we can get very good estimates of the true proportion of "yes" respondents.

## What are Randomised Responses?

The idea comes from a 1965 paper, in which author Stanley L Warner proposed a way to obfuscate responses of a survey by letting users


```{r coinflip, echo=FALSE}
shinyAppDir(
  "coinflip",
  options = list(
    width = "100%", height = 700
  )
)
```

## Drawbacks

This methodology increases the uncertainty of the answers, and is only useful when the sample size is large. 

However, when the behvaiour we're investigating is rare and the population is small, signal becomes impossible to detect from the noise. 

To visualise this phenomenon we employ an illustration using the VIC dataset on young drug users in schools.

https://discover.data.vic.gov.au/dataset/vcams-proportion-of-young-people-who-have-ever-used-marijuana-or-other-illegal-drugs


The Victorian Student Health and Wellbeing Survey (VSHAWS) also known as ‘About You’ conducted a survey of approximately 6,000 students 
from 264 Victorian schools, in Years 5, 8 and 11. Participants were given a non disclosure promise but what if they had underwent the randomized response
survey instead?

Below are simulations of what the outcomes would be if students had participated in randomized response surveys instead.

```{r drugs, echo=FALSE}
shinyAppDir(
  "drugs",
  options = list(
    width = "100%", height = 550
  )
)
```


## Bibliography:
https://www.jstor.org/stable/2283137
https://imai.fas.harvard.edu/research/files/randresp.pdf


