---
title: "Perfectly-Secure Multiparty Surveying"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal

A demonstration of how groups of people can be surveyed in a provably trustless and anonymous manner without added uncertainty.

### Polynomials

Polynomials are functions of the form:

$$f(x) = ax^2 +bx+c$$
There are 2 properties of polynomials that we care about:

1. Polynomials of degree T can be uniquely defined by T+1 unique points on the function through the use of Lagrange Polynomial interpolation.
2. The set of polynomials of degree T is closed under addition.

Together they let us use BGW Protocol for Perfectly-Secure Multiparty Surveying.
 
## What is the BWG Protocol?

The idea comes from a 1988 paper, in which the authors (Ben-Or. M , Goldwasser. S, Wigderson. A) proposed a way to sum the the numbers of N participants without any member divulging their own number. 

Procedure:

1. Let there be 3 participants.
2. Let each participant generate a random polynomial $r$ that has value $r(0) = 1$ if they want to answer YES and $r(0)=0$ if they want to answer NO.
3. Instruct the participants to keep their polynomials to themselves. Let's call user_A's polynomial: A, user_B's polynomial B and so forth.
4. Let user_A give the evaluation of A(2) to user_B and A(3) to user_C.
5. Let user_B give the evaluation of B(1) to user_B and B(3) to user_C.
6. Let user_C give the evaluation of C(1) to user_A and C(2) to user_B.
7. Instruct participants to keep the shared values to themselves.
8. Now we try to find f(x) = A(x)+B(x)+C(x), another 2nd degree polynomial by the 2nd property of polynomials.
9. Since user_A has A(1),B(1),C(1), they know f(1) and so broadcasts the value f(1).
10. Since user_B has A(2),B(2),C(2), they know f(2) and so broadcasts the value f(2).
11. Since user_C has A(3),B(3),C(3), they know f(3) and so broadcasts the value f(3).
12. Now that f(1),f(2),f(3) are public knowledge, we can use the 1st property of polynomials to find f.
13. Evaluate f(0). This is the sum of all the people who answered yes to the survey (A(0)+B(0)+C(0))






```{r polynomials, echo=FALSE}
shinyAppDir(
  "polynomials",
  options = list(
    width = "100%", height = 1200
  )
)
```


## Drawbacks
What we have demonstrated is a simplified version of what is introduced by BWD 1988. It illustrates the key principles of the BWG protocol and suffices for application among honest and non malicious parties.

However, if the group is contaminated we suffer 2 main problems:

1. Easy to sabotage. 
2. Misreporting


The protocol introduced in the paper extends on this to have amazing properties in:

1. Private Channels.
2. Semi honest Parties.
3. Malicious Parties.

## Speed Complexity.

Say we want to do a survey using this method on a million participants. That group can be partitioned to groups of size 10, such that only 10,000,000 messages need to be sent between participants. 

Partitioning has the added benefit, for this naive approach, of not allowing contaminated results to leak into other partitions.

## Citations

1. [Completeness Theores for the Non-Cryptographic Fault-Tolerant Distirbuted Computation](https://www.math.ias.edu/~avi/PUBLICATIONS/MYPAPERS/GBW88/GBW88.pdf)
2. [A Full Proof of the BGW Protocol for Perfectly-SecureMultiparty Computation](https://eprint.iacr.org/2011/136.pdf)
