---
title: "Perfectly-Secure Multiparty Surveying"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal

A demonstration of how groups of people can be surveyed in a provably trustless and anonymous manner without added uncertainty.

### Polynomials

Polynomials are functions of the form:
$$f(x) = ax^2 +bx+c$$
There are 3 properties of polynomials that we care about:

1. Polynomials of degree T can be uniquely identified by T+1 unique points on the function through the use of Lagrange Polynomial interpolation.
2. The set of polynomials of degree T is closed under addition.

Together they let us use BGW Protocol for Perfectly-Secure Multiparty Surveying.
 
## What is the BWG Protocol?

The idea comes from a 1988 paper, in which the authors (Ben-Or. M , Goldwasser. S, Wigderson. A) proposed a way to sum the the numbers of N participants without any member divulging their own number. 



```{r polynomials, echo=FALSE}
shinyAppDir(
  "polynomials",
  options = list(
    width = "100%", height = 1200
  )
)
```

## Drawbacks
What we have demonstrated is a simplified version of what is introduced by BWD 1988. It illustrates the key principles of the BWG protocol and suffices for application among honest and non malicious parties.

However, if the group is contaminated we suffer 2 main problems:

1. Easy to sabotage. 
2. Misreporting


The protocol introduced in the paper extends on this to have amazing properties in:

1. Private Channels.
2. Semi honest Parties.
3. Malicious Parties.


## Bibliography

https://www.math.ias.edu/~avi/PUBLICATIONS/MYPAPERS/GBW88/GBW88.pdf
https://eprint.iacr.org/2011/136.pdf
https://rpubs.com/aaronsc32/lagrangian-polynomial-interpolation-r


